Towards Correct Legion

### 2017-08-26 correctnesshpc/paper.tex
George edits 2.1

Given the importance of importance of HPC systems to issues of both national and
economic security being able to efficiently and correctly specify, develop and
validate these systems is an important research challenge with impacts 
ranging from climate modeling to nuclear safety.

Formal specification and code proved by formal methods such as program logics
provide the strongest guarantees of correctness. Specifications describe of how a program
should behave, while proofs show that a implementations conform to
their specifications. These \emph{formal} specifications and proofs 
have been embedded in a machine-checked formal
logic \cite{bertot2013interactive, nipkow2002isabelle, pfenning1999system,
jackson1994nuprl}. This process of formalizing specifications and proofs in
machine checked logics has been shown to catch common errors in previously
informal proofs, and therefore provide higher 
assurance of correctness than alternative methods \cite{clarke1996formal,
yang2011finding}.

@@

The theorems we are using are described in Figure~\ref{soundnesstheorem} and
Figure~\ref{completenesstheorem} (see \texttt{https://github.com/lanl/formallegion}
for Coq versions of the proofs).

\begin{figure}
\begin{BVerbatim}
Theorem preservation : forall (e5:e) (t:T) (E:E) (M:M) 
(L:L) (H:H) (S:list (e * e)) (C:list e) (T:T),
    exists v,
      eval M L H S C e5 v E ->
      typing NilContext NilPriv NilConstraint e5 T  ->
      exists G P Omega T, typing G P Omega v T.
\end{BVerbatim}
\caption{soundness theorem}
\label{soundnesstheorem}
\end{figure}

\begin{figure}
\begin{BVerbatim}
Theorem progress : forall  (e5:e) (t:T) (M:M) (H:H)  
(C:list e) (T1 T2:T) L (S:list (e * e)),
    typing NilContext NilPriv NilConstraint e5 T1  ->
    (exists E v ,
        is_value v ->
        eval M L H S C e5 v E).
\end{BVerbatim}
\caption{completeness theorem}
\label{completenesstheorem}
\end{figure}

>>>>

Given the importance of importance of HPC systems to issues of both national
and economic security, being able to efficiently and correctly specify,
develop, and validate these systems is an important research challenge with
impacts ranging from climate modeling to nuclear safety.

Formal specification and code proved by formal methods such as program logics
provide the strongest guarantees of correctness. Specifications describe how
a program should behave, while proofs show that a implementations conform to
their specifications. \emph{Formal} specifications and proofs are those that
have been embedded in a machine-checked formal logic
\cite{bertot2013interactive, nipkow2002isabelle, pfenning1999system,
jackson1994nuprl}. This process of formalizing specifications and proofs in
machine checked logics has been shown to catch common errors in previously
informal proofs, and therefore provide higher assurance of correctness than
alternative methods \cite{clarke1996formal, yang2011finding}.

@@

The theorems we are using are described in Figure~\ref{soundnesstheorem} and
Figure~\ref{preservationtheorem} (see \texttt{https://github.com/lanl/formallegion}
for Coq versions of the proofs).

\begin{figure}
\begin{BVerbatim}
Theorem preservation : ∀ e t E M L H S C T,
  ∃ v,
    eval M L H S C e v E →
    typing [] [] [] e T → 
    ∃ G P Ω, typing G P Ω v T.
\end{BVerbatim}
\caption{Preservation theorem}
\label{preservationtheorem}
\end{figure}

\begin{figure}
\begin{BVerbatim}
Theorem soundness : ∀ e t M H C T1 T2 L S,
  typing [] [] [] e T1  →
  (∃ E v,
    is_value v →
    eval M L H S C e v E).
\end{BVerbatim}
\caption{Soundness theorem}
\label{soundnesstheorem}
\end{figure}
